Contracts for Contracts

### 2023-06-03 paper/contract_solidity.tex
misc

\section{Contract Solidity by Examples}

In this section, we introduce \lang informally with examples.
\lang is a non-breaking extension that additionally provides means
to specify behavioral contracts on top of the Solidity language.
We provide a brief introduction of Solidity first, then discuss our extension
of behavioral contracts.
We often use \emph{specification} for behavioral contracts to avoid terminological ambiguity.

\subsection{The Solidity Language}

@@

\subsubsection*{\textbf{\lang's Design Rationale}}
This paper concerns about designing an extension for Solidity that enhances the
language with higher-order temporal behavioral contracts.
The extension should be
\todo{non-intrusive, easy to use, expressive, gradual (you do not need to pay the overhead
	if you don't use contracts), efficient (little overhead)}

>>>>

\section{Background: The Solidity Language}

@@

\section{\lang by Examples}

In this section, we introduce \lang (Contract Solidity) informally with examples.
\lang is a non-breaking extension that additionally provides means
to specify behavioral contracts on top of the Solidity language.
We provide a brief introduction of Solidity first, then discuss our extension
of behavioral contracts.
We often use \emph{specification} for behavioral contracts to avoid terminological ambiguity.

\paragraph{\lang's Design Rationale}
This paper concerns about designing an extension for Solidity that enhances the
language with higher-order temporal behavioral contracts.
The extension should be
\todo{non-intrusive, easy to use, expressive, gradual (you do not need to pay the overhead
	if you don't use contracts), efficient (little overhead)}

### 2023-06-03 paper/implementation.tex
misc

the implementation that modifies the off-the-shelf Solidity compiler that
supports contracts and generates code with correct contracts checking

\todo{what we didn't handle: inlined assembly, and ??? }

>>>>

We implement \lang as a preprocessor of Solidity programs annotated with
\lang's specifications (\todo{bwd ref}). Given a such input program, \lang analyzes where and
which condition needs to be inserted into the original program.
The output program can be compiled and deployed using downstream Solidity
toolchains without any further modification.

Our current implementation does not handle inlined assembly. \todo{why}

Contracts for higher-order functions is another future work when Solidity has a
proper support for lambda expressions. Without such proper support from the base language,
\todo{...}
